DeepSphere: a graph-based spherical CNN

### 2019-09-24 main.tex

\section{Proof of theorem}\label{sec: appendix: proof of theorem}
Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal M$, a smooth function $f:\mathcal M \rightarrow \mathbb R$, and defined the vector $\b f$ of samples of $f$ as follows: $\b f\in \mathbb R^n,\ \b f_i = f(x_i)$, it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
where $L_n^t$ is defined as follows:
\begin{definition}{}
	\label{def:Heat Kernel Graph Laplacian operator}
	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
\end{definition}
Thus, to prove theorem \ref{theo:pointwise convergence for a regular sampling} it will be sufficient to prove that 
\begin{equation}\label{eq:continuous convergence}
 \lim_{n\to\infty} \frac{|\mathbb{S}^2|}{4\pi t_n^2} {L}_n^{t_n} f(y) =  \Delta_{\mathbb{S}^2}f(y)
\end{equation}
For the sake of the proof we will need also the following facts:
\begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$. We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\label{def:Functional approximation to the Laplace-Beltrami operator}
	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
\end{definition}

\begin{prop} (\cite{belkin2005towards}) \\
Let $\mathcal M$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb R^N$, and fix $y\in\mathcal M$. Let the data points $x_1, \dots, x_n$ be sampled form a uniform distribution on the manifold $\mathcal M$. Set $t_n=n^{-\frac{1}{k+2+\alpha}}$, for any $\alpha>0$ and let $f\in\mathcal C_\infty(\mathcal M)$. Then
	$$\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\triangle_{\mathcal M}f(y).$$
	\label{prop:3}
\end{prop}

% brief introduction:
This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}. This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

Our first goal is thus to prove the following Proposition:
\vspace{0.5cm}
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $||\cdot||$ with Lipschitz constant $\mathcal L_f$
	$$
	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
	$$
	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
\end{prop}
\vspace{0.5cm}

@@

\subsubsection*{HEALPix}

@@

30 epochs with augmented dataset, 3 random translation perturbation, or 90 epochs over dataset that can be augmented
\subsubsection*{Equiangular}
Equiangular sampling with bandwidth of 64 in longitude and latitude.
The architecture of the Neural Network is exactly the same, with a stride of [2, 2] for each pooling layer
\subsection{cosmo}
HEALPix sampling, Nside = 1024, with improved graph

@@

\begin{table}
    \centering
	\begin{tabular}{l l l l l}
		\toprule
        & TC & AR & BG & mean \\
		\midrule
		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
		\midrule
		DS (Jiang architecture, weighted loss) & 97.1 & 97.6 & 96.5 & 97.1 \\
        DS (weighted loss) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
		DS (wider architecture, weighted loss) & 91.5 & 93.4 & 99.0 & 94.6 \\
		\midrule
        DS (Jiang architecture, non-weighted loss) & 33.6 & 93.6 & 99.3 & 75.5 \\
        DS (non-weighted loss) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
        DS (wider architecture, non-weighted loss) & 73.4 & 92.7 & 99.8 & 88.7 \\
		\midrule
		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS (Cohen architecture, non-weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: accuracy.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
		\label{tab:climate:accuracy}
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l l l l}
		\toprule
        & TC & AR & mean \\
		\midrule
		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
		\midrule
        DS (Jiang architecture, non-weighted loss) & 46.2 & 93.9 & 70.0 \\
        DS (non-weighted loss) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
        DS (wider architecture, non-weighted loss) & 84.71 & 98.05 & 91.38 \\
		\midrule
        DS (Jiang architecture, weighted loss) & 49.7 & 89.2 & 69.5 \\
        DS (weighted loss) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
        DS (wider architecture, weighted loss) & 52.80 & 94.78 & 73.79 \\
		\midrule
		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: average precision.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes.
		Note that a weighted cross-entropy loss is not optimal for the average precision metric.
	}
		\label{tab:climate:map}
\end{table}

@@

\subsubsection*{Icosahedron}

@@

30 epochs
\subsubsection*{DS-jiang}
encoder:\\
\begin{dmath}
    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
\end{dmath}
decoder:\\
\begin{dmath}
    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
\end{dmath}
% number of parameters: 590'976  % more feat is 16 times more

concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
\subsubsection*{Equiangular}
Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.

@@

\subsubsection*{Results}

\subsubsection*{Dense}

@@

\subsubsection*{Global}

>>>>

\section{Proof of theorem \ref{theo:pointwise convergence for a regular sampling}}\label{sec: appendix: proof of theorem}

\paragraph{Preliminaries.}
The proof of theorem \ref{theo:pointwise convergence for a regular sampling} is inspired from the work of \cite{belkin2005towards}. As a result, we start by restating some of their results.
Given a sampling $V = \{x_i\in\mathcal M\}_{i=0}^{n-1}$ of a closed, compact and infinitely differentiable manifold $\mathcal{M}$, a smooth ($\in\mathcal{C}_\infty(\mathcal{M)}$) function  $f:\mathcal{M} \rightarrow \mathbb{R}$, and defined the vector $\b{f}$ of samples of $f$ as follows: $T_Vf=\b{f} \in \mathbb{R}^n,\ \b{f}_i = f(x_i)$.
The proof is constructed by leveraging 3 different operators:
\begin{itemize}
    \item The extended graph Laplacian operator is a functional $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$  is defined given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ and $y\in \mathcal{M}$  as
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^tf(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
	Note that we have the following relation $\b{L}_n^t \b{f} = T_V L_n^t f$.
	\item The functional approximation to the Laplace-Beltrami operator is a functional $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ defined  as
	\begin{equation}
    \label{eq:Functional approximation to the Laplace-Beltrami operator}
	L^tf(y) = \int_{\mathcal{M}} \exp^{-\frac{\|y-x\|^2}{4t}}\left(f(y)-f(x)\right)d\mu(x),
	\end{equation}
	where given $\mu$ be the uniform probability measure on the manifold $\mathcal{M}$, and let $\text{vol}(\mathcal{M})$ be the volume of $\mathcal{M}$.
	\item 
	The Laplace-Beltrami operator $\Delta_{\mathcal{M}}$ is defined as the divergence of the gradient
	\begin{equation}
        \label{eq:laplace-beltrami}
        \Delta_{\mathcal M}f(y):= -\text{div}(\nabla_{\mathcal M}f)
    \end{equation}
    of a differentiable function $f: \mathcal M\rightarrow \mathbb R$. The gradient $\nabla f: \mathcal M \rightarrow T_p\mathcal M$ is a vector field defined on the manifold pointing towards the direction of steepest ascent of $f$, where $T_p\mathcal M$ is the affine space of all vectors tangent to $\mathcal M$ at $p$

\end{itemize}

Leaveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian toward the Laplace-Beltrami operator.
The proofs consists in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges toward \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).    
\end{equation}
\label{prop:3}
\end{prop}

\paragraph{Building the proof.}
As the sphere is a compact smooth manifold embedded in $\mathbb{R}^3$, we can reuse the second part or their proofs where \eqref{eq:Functional approximation to the Laplace-Beltrami operator} $\rightarrow$ \eqref{eq:laplace-beltrami}.
Thus, our strategy to prove Theorem \ref{theo:pointwise convergence for a regular sampling} is to a) show that 
\begin{equation}\label{eq:continuous convergence}
 \lim_{n\to\infty}L_n^{t} f(y) =  L^t(y)
\end{equation}
for a particular class of sampling and b) apply Proposition \ref{prop:3}.

%  \frac{|\mathbb{S}^2|}{4\pi t} 
% \begin{definition}{}\\
% 	\label{def:Heat Kernel Graph Laplacian operator}
% 	\text{Given a sampling $\{x_i\in\mathcal M\}_{i=0}^{n-1}$ of the manifold we define the \textbf{operator} }$L_n^t$ such that
% 	$$L_n^tf(y) := \frac{1}{n}\left[ \sum_{i=0}^{n-1} \exp \left\{ {-\frac{||x_i-y||^2}{4t}}\right\}\left(f(y)-f(x_i)\right)\right]$$
% \end{definition}

% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\mathbb S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\mathbb S^2}f(x)$
% where $L_n^t$ is defined as follows:

% For the sake of the proof we will need also the following facts:
% \begin{definition}{} (\cite{belkin2005towards})\\ \label{eq: my L^t} Let $\mu$ be the uniform probability measure on the manifold $\mathcal M$, and let $\text{vol}(\mathcal M)$ be the volume of $\mathcal M$. We define the functional approximation to the Laplace-Beltrami operator to be the operator $L^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
% 	\label{def:Functional approximation to the Laplace-Beltrami operator}
% 	$$ L^tf(y) = \int_{\mathcal M}\exp\left\{-\frac{||y-x||^2}{4t}\right\}\left(f(y)-f(x)\right)d\mu(x)$$
% \end{definition}

% brief introduction:
% This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}. This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

We start by proving the following Proposition:
\vspace{0.5cm}
\begin{prop}\label{prop:1}
	For an equal area sampling $\{x_i\in\mathbb S^2\}_{i=0}^{n-1}: A_i=A_j \forall i,j$ of the sphere it is true that for all $f: \mathbb S^2 \rightarrow \mathbb R$ Lipschitz with respect to the Euclidean distance $\|\cdot\|$ with Lipschitz constant $\mathcal L_f$
	$$
	\left| \int_{\mathbb S^2}f({ x})\text{d}{\mu(x)} - \frac{1}{n}\sum_i f( x_i)\right|\leq \mathcal L_fd^{(n)}.
	$$
	Furthermore, for all $y\in\mathbb S^2$ the Heat Kernel Graph Laplacian operator $L^t_n$ converges pointwise to the functional approximation of the Laplace Beltrami operator $L^t$
	$$ L_n^tf(y)\xrightarrow{n\to\infty} L^tf(y).$$
\end{prop}
\vspace{0.5cm}

@@

\subsubsection*{HEALPix architecure}

@@

30 epochs with augmented dataset, 3 random translation perturbation (same as 90 epochs over dataset with 3 possible random rotation)
\subsubsection*{Equiangular architecture}
Equiangular sampling with bandwidth of 64 in longitude and latitude.
The architecture of the Neural Network is exactly the same, with a stride of [2, 2] for each pooling layer
\subsection{cosmo}
HEALPix sampling, Nside = 1024, with improved graph

@@

\begin{table}
    \centering
	\begin{tabular}{l l l l l}
		\toprule
        & TC & AR & BG & mean \\
		\midrule
		\cite{mudigonda2017climateevents} & 74 & 65 & 97 & 78.67 \\
		\cite{jiang2019sphericalcnn} (paper) & 94 & 93 & 97 & 94.67 \\
		\cite{jiang2019sphericalcnn} (rerun) & 93.9 & 95.7 & 95.2 & 94.95 \\
        \cite{cohen2019gauge} (S2R) & 97.8 & 97.3 & 97.3 & 97.5 \\
        \cite{cohen2019gauge} (R2R) & 97.9 & 97.8 & 97.4 & 97.7 \\
		\midrule
		DS (Jiang architecture, weighted loss) & 97.1 & 97.6 & 96.5 & 97.1 \\
        DS (weighted loss) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
		DS (wider architecture, weighted loss) & 91.5 & 93.4 & 99.0 & 94.6 \\
		\midrule
        DS (Jiang architecture, non-weighted loss) & 33.6 & 93.6 & 99.3 & 75.5 \\
        DS (non-weighted loss) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\
        DS (wider architecture, non-weighted loss) & 73.4 & 92.7 & 99.8 & 88.7 \\
		\midrule
		\todo{DS (Cohen architecture, weighted loss)} & 95.5 & 96.9 & 93.9 & 95.4 \\
		\todo{DS (Cohen architecture, non-weighted loss)} & 56.4 & 90.0 & 98.9 & 81.8 \\
		\todo{DS (full dataset, non-weighted loss)} & 31.3 & 75.2 & 99.9 & 68.80 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: accuracy.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes, against the background (BG).
		\todo{\citet{mudigonda2017climateevents} is not directly comparable as they don't use the same input feature maps.}
		Note that a non-weighted cross-entropy loss is not optimal for the accuracy metric.
		\label{tab:climate:accuracy}
	}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{l l l l}
		\toprule
        & TC & AR & mean \\
		\midrule
		\cite{jiang2019sphericalcnn} (rerun) & 11.08 & 65.21 & 38.41 \\
        \cite{cohen2019gauge} (S2R) & - & -& 68.6 \\
        \cite{cohen2019gauge} (R2R) & - & -& 75.9 \\
		\midrule
        DS (Jiang architecture, non-weighted loss) & 46.2 & 93.9 & 70.0 \\
        DS (non-weighted loss) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ \\
        DS (wider architecture, non-weighted loss) & 84.71 & 98.05 & 91.38 \\
		\midrule
        DS (Jiang architecture, weighted loss) & 49.7 & 89.2 & 69.5 \\
        DS (weighted loss) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ \\
        DS (wider architecture, weighted loss) & 52.80 & 94.78 & 73.79 \\
		\midrule
		\todo{DS (Cohen architecture, weighted loss)} & 13.1 & 80.3 & 46.7 \\
		\todo{DS (Cohen architecture, non-weighted loss)} & 59.8 & 85.0 & 72.4 \\
		\todo{DS (full dataset, non-weighted loss)} & 55.53 & 94.85 & 75.19 \\
		\bottomrule
    \end{tabular}
    \caption{
		Results on climate event segmentation: average precision.
		Tropical cyclones (TC) and atmospheric rivers (AR) are the two positive classes.
		Note that a weighted cross-entropy loss is not optimal for the average precision metric.
	}
		\label{tab:climate:map}
\end{table}

@@

\subsubsection*{DS Icosahedron architecture}

@@

30 epochs

wider architecture is the same, but with 2 time the feature maps.
\subsubsection*{DS (Jiang architecture)}
encoder:\\
\begin{dmath}
    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
\end{dmath}
decoder:\\
\begin{dmath}
    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
\end{dmath}
% number of parameters: 590'976  % more feat is 16 times more

concat the results of the corresponding encoder layer after the graph convolution. Similar to ``Jiang et al.''
\subsubsection*{Full dataset - Equiangular architecture}
Equiangular sampling, with a latitude bandwidth 384 and longitude bandwidth 576.

@@

\subsubsection*{Deatilled results}

\subsubsection*{Dense task architecture}

@@

\subsubsection*{Global task architecture}
